### 2017-11-09 UOW_thesis_template_v2-0/thesis_template/chapters/Intro.tex
:art: Adding corrections from Matt Davison

	A well-known result for determining the option value is known as the Black-Scholes formula \cite{Black1973}. The Black-Scholes formula is in fact a partial differential equation (PDE) that is also paired with a terminal condition governed by a payoff function. The payoff function merely states what the option's value will be at the expiry date. Typically, this is normally a piecewise linear function of the strike price and the underlying asset (at least in terms of a call and put). One of the most classical methods to solve the Black-Scholes PDE system is to invoke a transformation of variables (further details of this in addition to~\cite{Black1973} can be found in~\cite{Wilmott1995}) that effectively eliminates a few terms and reduces the PDE system to the archetypal heat equation commonly seen in thermodynamics~\cite{cannon1984one}. The motivation for this step is because the heat equation has been studied endlessly in literature and the solution to the PDE system is ascertainable~\cite{Churchill1938}. The original details of~\cite{Black1973} can also be complemented with~\cite{Wilmott1995} for further details and discussion about this derivation. The crux of option valuation is to determine a fair price for the holder to pay the writer to enter into their specified contract. This price is commonly known as the \emph{option premium} (or simply, the premium) that actually signifies the value of the option at time-zero (i.e., starting today).

@@

Although this clever investment strategy of emulating an American put option using cash flows is financially instructive, it does not provide any insight into the properties of the optimal exercise boundary. It was not until the work of Kim~\cite{Kim1990} that not only provided a continuous time solution to the work in~\cite{Geske1984}, but also contained a representation of the American call option as a sum of the European call option plus an additional component that exemplifies the gains one would make from potential early exercise. This term is known as the \emph{early exercise premium}. Moreover, this early exercise premium is expressed in terms of an integral which encapsulates the optimal exercise boundary. If paired with the appropriate boundary conditions with the PDE, one arrives at an integral equation (depending on which type of option is chosen) for the optimal exercise boundary which can then be solved using numerical procedures that involve both a root-finding scheme like Newton-Raphson and numerical integration like a standard quadrature scheme (e.g., Trapezoidal). The aforementioned boundary conditions for the option to determine this integral equation for the free boundary are also known as the \emph{smooth pasting conditions} or matching conditions, and it is meant to mathematically ensure the optimality of the free boundary. The consequent intuitive outcomes by Kim later become coined ``Kim's equations'' or ``Kim's integral equations''. Solving the integral equation related to the optimal free boundary is ideal because if that is completed, then the early early exercise premium is also computable and thus, one would be able to obtain the time-zero American option value. As a response to this, several authors have devoted time to investigate and devise algorithms that would solve this integral equation for the exercise premium (in particular, see~\cite{Huang1996, Press1992, Sevcovic2001} just to list a few examples).

@@

Briefly returning to the analytical side, Cheang and Chiarella \cite{Cheang2011} advocated for amendments to be made to Merton's original jump-diffusion model. They argued that the Merton model makes assumptions that lead to the jump-risk~\cite{Gibson2001} being unpriced and force the distribution of the Poisson jumps to remain unchanged under a change of measure. The authors stressed the significance of this since a realistic market which contains assets with jumps is incomplete. Additionally, when the market price of the jump-risk is accounted for, there exist many equivalent martingale measures that ultimately produce different prices for options. Hence, they introduced a Radon-Nikod\'{y}m derivative process which translates the market measure to an equivalent martingale measure (EMM) for option valuation. However, the EMM is non-unique in the presence of jumps; one must choose parameters in the Radon-Nikod\'{y}m derivative to establish an EMM to price options. Furthermore, Cheang and Chiarella derived a PIDE and thus a general pricing formula which reduces to Merton's solution \cite{Merton1976} as a special case.

Frontczak \cite{Frontczak2013} adopted a method of solving the PIDE seen in \cite{Merton1976} using Mellin transforms. He proceeded to re-derive Merton's solution for a European put option via direct inversion. Frontczak's approach of directly evaluating of the inverse Mellin integral (i.e., a complex integral) \textcolor{black}{is where the approach could be improved}. Moreover, this process needs to be repeated for different payoffs, making this procedure computationally expensive and tedious.

@@

		The implied volatility content commences in chapter 4, where our main focus is determining an expression for the implied volatility under the assumption that jumps are present in the underlying asset price process. We begin by deriving a Dupre-like PIDE. This is then followed by deriving the implied volatility formula required. Once again, this is under jump-diffusion dynamics. Numerics will be analysed and investigated to assess the potential application of the aforementioned results. Finally, we will present a discussion of the findings followed by a conclusion with tentative future directions.

		As an extension to the work in chapter 3, we will be investigating the jump-diffusion model for American options in chapter 5. Specifically, the main focus here will be to develop a method and associated algorithm to solve for the optimal moving boundary (or exercise boundary) that separates the continuation and stopping/exercise regions for American options. The result is an approximate ordinary differential equation that is similar in form to the one Rodrigo derived in~\cite{Rodrigo2013}. The accuracy of this new system will be compared against a the finite-difference method for American options in jump-diffusion dynamics. This is then succeeded by a discussion of the findings and concluding remarks.

>>>>

	A well-known result for determining the option value is known as the Black-Scholes equation \cite{Black1973}. The Black-Scholes formula is in fact a partial differential equation (PDE) that is also paired with a terminal condition governed by a payoff function. The payoff function merely states what the option's value will be at the expiry date. Typically, this is normally a piecewise linear function of the strike price and the underlying asset (at least in terms of a call and put). One of the most classical methods to solve the Black-Scholes PDE system is to invoke a transformation of variables (further details of this in addition to~\cite{Black1973} can be found in~\cite{Wilmott1995}) that effectively eliminates a few terms and reduces the PDE system to the archetypal heat equation commonly seen in thermodynamics~\cite{cannon1984one}. The motivation for this step is because the heat equation has been studied endlessly in literature and the solution to the PDE system is ascertainable~\cite{Churchill1938}. The original details of~\cite{Black1973} can also be complemented with~\cite{Wilmott1995} for further details and discussion about this derivation. The crux of option valuation is to determine a fair price for the holder to pay the writer to enter into their specified contract. This price is commonly known as the \emph{option premium} (or simply, the premium) that actually signifies the value of the option at time-zero (i.e., starting today).

@@

Although this clever investment strategy of emulating an American put option using cash flows is financially instructive, it does not provide any insight into the properties of the optimal exercise boundary. It was not until the work of Kim~\cite{Kim1990} that not only provided a continuous time solution to the work in~\cite{Geske1984}, but also contained a representation of the American call option as a sum of the European call option plus an additional component that exemplifies the gains one would make from potential early exercise. This term is known as the \emph{early exercise premium}. Moreover, this early exercise premium is expressed in terms of an integral which encapsulates the optimal exercise boundary. If paired with the appropriate boundary conditions with the PDE, one arrives at an integral equation (depending on which type of option is chosen) for the optimal exercise boundary which can then be solved using numerical procedures that involve both a root-finding scheme like Newton-Raphson and numerical integration like a standard quadrature scheme (e.g., Trapezoidal). The aforementioned boundary conditions for the option to determine this integral equation for the free boundary are also known as the \emph{smooth pasting conditions} or matching conditions, and it is meant to mathematically ensure the optimality of the free boundary. The consequent intuitive outcomes by Kim later become coined ``Kim's equations'' or ``Kim's integral equations''. Solving the integral equation related to the optimal free boundary is ideal because if that is completed, then the early exercise premium is also computable and thus, one would be able to obtain the time-zero American option value. As a response to this, several authors have devoted time to investigate and devise algorithms that would solve this integral equation for the exercise premium (in particular, see~\cite{Huang1996, Press1992, Sevcovic2001} just to list a few examples).

@@

Briefly returning to the analytical side, Cheang and Chiarella \cite{Cheang2011} advocated for amendments to be made to Merton's original jump-diffusion model. They argued that the Merton model makes assumptions that lead to the jump-risk~\cite{Gibson2001} being unpriced and force the distribution of the Poisson jumps to remain unchanged under a change of measure. The authors stressed the significance of this since a realistic market which contains assets with jumps is incomplete. Additionally, when the market price of the jump-risk is accounted for, there exist many equivalent martingale measures that ultimately produce different prices for options. Hence, they introduced a Radon-Nikod\'{y}m derivative process which translates the market measure to an equivalent martingale measure (EMM) for option valuation. However, the EMM is non-unique in the presence of jumps; one must choose the parameters in the Radon-Nikod\'{y}m derivative to establish an EMM to price options. Furthermore, Cheang and Chiarella derived a PIDE and thus a general pricing formula which reduces to Merton's solution \cite{Merton1976} as a special case.

Frontczak \cite{Frontczak2013} adopted a method of solving the PIDE seen in \cite{Merton1976} using Mellin transforms. He proceeded to re-derive Merton's solution for a European put option via direct inversion. Frontczak's approach of directly evaluating the inverse Mellin integral (i.e., a complex integral) \textcolor{black}{is where the approach could be improved}. Moreover, this process needs to be repeated for different payoffs, making this procedure computationally expensive and tedious.

@@

		The implied volatility content commences in chapter 4, where our main focus is determining an expression for the implied volatility under the assumption that jumps are present in the underlying asset price process. We begin by deriving a Dupire-like PIDE. This is then followed by deriving the implied volatility formula required. Once again, this is under jump-diffusion dynamics. Numerics will be analysed and investigated to assess the potential application of the aforementioned results. Finally, we will present a discussion of the findings followed by a conclusion with tentative future directions.

		As an extension to the work in chapter 3, we will be investigating the jump-diffusion model for American options in chapter 5. Specifically, the main focus here will be to develop a method and associated algorithm to solve for the optimal moving boundary (or exercise boundary) that separates the continuation and stopping/exercise regions for American options. The \ref{?}sult is an approximate ordinary differential equation that is similar in form to the one Rodrigo derived in~\cite{Rodrigo2013}. The accuracy of this new system will be compared against a the finite-difference method for American options in jump-diffusion dynamics. This is then succeeded by a discussion of the findings and concluding remarks.

### 2017-11-09 UOW_thesis_template_v2-0/thesis_template/chapters/Preliminaries.tex
Fixed up last corrections given by Marianito
:art: Adding corrections from Matt Davison

We will now construct the foundation needed to tackle the American option pricing problems in this thesis.
As aforementioned in the introduction, there are a multitude of ways to formulate the American option pricing problem.
The structure we will present provides a clear interpretation of all the possible scenarios that can occur with American options.

Due to the liberty of being able to exercise the option early, the American option valuation problem involves two unknown functions: the option value itself $V_t$ and
the function $S^*$ which is commonly denoted as the \emph{optimal exercise boundary}~\cite{Kwok2008}. For an American put option, the goal is to ascertain
$v_\text{a}^{\text{put}} =v_\text{a}^{\text{put}}(x,t)$ and $S^* = S^*(t)$ such that
	\begin{enumerate}
			\item $\mathscr{L}v_\text{a}^{\text{put}}(x,t) = 0, \quad x > S^*(t)$,
			\item $v_\text{a}^{\text{put}}(x,t) = K - x, \quad 0 \leq x < S^*(t)$,
	\end{enumerate}
	with a payoff $v_\text{a}^{\text{put}}(x,T) = \max(K-x,0)$. For $x = S^*(t)$, we will introduce continuity conditions which in the literature are regularly referred to as \emph{smooth pasting conditions}. For the American put, these are
		\begin{equation*}
			v_\text{a}^{\text{put}}(S^*(t),t) = K - S^*(t), \quad \fr{\pr v_\text{a}^{\text{put}}}{\pr x}(S^*(t),t) = -1.
		\end{equation*}
	From this formulation, we can view the smooth pasting conditions as reflecting the interests of option holders to maximize their profit. The value of the asset will dictate what choice the holders should make due to the additional unknown $S^*(t)$ as seen above in the problem formulation . For an American put, the interval $0 \leq x < S^*(t)$ is known as the \emph{exercise region} as it is the most optimal time to exercise the option irrespective of time to expiry since the value of the American put is equal to its payoff. In contrast, $x > S^*(t)$ represents the \emph{continuation region} where the American put is worth more than its payoff and thus is more valuable to continue to hold the option. As we have mentioned in the introduction, the position of $S^*(t)$ (which divides the $x$ domain into the exercise and continuation regions) is unknown \emph{a priori} which adds another layer of difficulty to the option pricing problem.

@@

\section{Useful properties of the CDF of a standard normal variable}
Several properties of the cumulative normal distribution $N$ and its derivative $N'$ will also be required~\cite[pp. 235--239]{Jeff1995}, namely
	\begin{equation}
		\begin{split}
		N(x) = \fr{1}{\sqrt{2\pi}}\int_{-\infty}^x e^{-y^2/2} & \, \d y, \quad %= \fr{1}{2} + \fr{1}{2}\text{erf}\left(\fr{x}{\sqrt{2}}\right) \\
		N(-x) = 1 - N(x), \quad
		N'(x) = \fr{1}{\sqrt{2\pi}}e^{-x^2/2} \label{eqn:Nprime}, \\
		&N(\infty) = 1, \quad N(-\infty) = 0.
		\end{split}
	\end{equation}
We also require the bivariate (standard) normal CDF~\cite{Genz2004}
	\begin{equation}
		\label{eqn:N2}
		N_2(x,y;\rho) = \fr{1}{2\pi\sqrt{1-\rho^2}}\int_{-\infty}^x\int_{-\infty}^y e^{-(u^2-2\rho uv + v^2)/(2(1-\rho^2))} \, \d v \, \d u,
	\end{equation}
where $\rho \in (-1,1)$ . It is not difficult to show that	
	\begin{equation}
		\label{eqn:Nspecial}
		\begin{split}
		&N_2(x,\infty;\rho) = N(x), \quad N_2(\infty,y;\rho) = N(y),\\
		&N_2(x,-\infty;\rho) = N_2(-\infty,y;\rho) = 0, \\
		&N_2(-\infty,\infty;\rho) = N_2(\infty,-\infty;\rho) = 0, \quad N_2(\infty,\infty;\rho) = 1.
		\end{split}
	\end{equation}
\section{Lemmas and corollaries we will need}
The following lemmas and corollaries will also be of great use throughout this thesis:
\subsection{General lemmas}
	\begin{lemma}
		\label{lem:2}
	For $a > 0$ and $b \in \mathbb{R}$, we have
	\begin{equation*}
		\M^{-1}\left\{ e^{-b\xi/a}e^{\xi^2/(2a^2)} \right\} = aN'(a\log x + b).
	\end{equation*}
	\end{lemma}
\begin{proof}
	See Appendix A.1.
\end{proof}
	\begin{lemma}
		\label{lem:1}
		For $a_1, \, a_2 > 0$ and $b_1, \, b_2 \in \mathbb{R}$, we have
			\begin{align*}
				&\int_0^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right).
			\end{align*}
	\end{lemma}
	\begin{proof}
		See Appendix A.2.
	\end{proof}
	\begin{lemma}
		\label{lem:2b}
		For $a_1, \, a_2 > 0$, $b_1, \, b_2 \in \mathbb{R}$, and $c > 0$, it follows from that
		\begin{align*}
			&\int_c^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right)N(d),
		\end{align*}
		where
		$$
			d = \sqrt{a_1^2+a_2^2}\left( \log(1/c) + \fr{b_2}{a_2} - \fr{a_1\gamma}{a_1^2+a_2^2} \right), \quad
			\gamma = \fr{a_1b_2}{a_2} + b_1.
		$$
	\end{lemma}
	\begin{proof}
		See Appendix A.3.
	\end{proof}

@@

			e^{\int_{t_1}^{t_2} r(\tau) \, \d\tau}\int_{a_1}^{b_1} \fr{1}{y} \K\left( \fr{x}{y}, t_1, t_2 \right) \, \d y \enskip = N\left( z_2\left( \fr{x}{a_1},t_1,t_2 \right) \right) - N\left( z_2\left( \fr{x}{b_1},t_1,t_2 \right) \right)

@@

			& \qquad  N_2\left( z_2\left( \fr{x}{b_1}, t_1, t_2 \right), z_2\left( \fr{x}{b_2}, t_1, t_3 \right); \rho  \right) + N_2\left( z_2\left( \fr{x}{a_1}, t_1, t_2 \right), z_2\left( \fr{x}{a_2}, t_1, t_3 \right); \rho  \right) \\

@@

where we define $\K_d$ to be the \emph{discretised Black-Scholes kernel} given by

@@

The reasoning for ``discretised'' is because~\eqref{eqn:Kd} will be primarily used for pricing compound options where an underlying pays one discrete dividend.

>>>>

We will now construct the foundation needed to tackle the American option pricing problems in this thesis.
As mentioned in the introduction, there are a multitude of ways to formulate the American option pricing problem.
The structure we will present provides a clear interpretation of all the possible scenarios that can occur with American options.

Due to the liberty of being able to exercise the option early, the American option valuation problem involves two unknown functions: the option value itself $V_t$ and
the function $S^*$ which is commonly denoted as the \emph{optimal exercise boundary}~\cite{Kwok2008}. For an American put option, the goal is to ascertain
$v_\text{a}^{\text{put}} =v_\text{a}^{\text{put}}(x,t)$ and $S^* = S^*(t)$ such that
	\begin{enumerate}
			\item $\mathscr{L}v_\text{a}^{\text{put}}(x,t) = 0, \quad x > S^*(t)$,
			\item $v_\text{a}^{\text{put}}(x,t) = K - x, \quad 0 \leq x < S^*(t)$,
	\end{enumerate}
	with a payoff $v_\text{a}^{\text{put}}(x,T) = \max(K-x,0)$. For $x = S^*(t)$, we will introduce continuity conditions which in the literature are regularly referred to as \emph{smooth pasting conditions}. For the American put, these are
		\begin{equation*}
			v_\text{a}^{\text{put}}(S^*(t),t) = K - S^*(t), \quad \fr{\pr v_\text{a}^{\text{put}}}{\pr x}(S^*(t),t) = -1.
		\end{equation*}
	From this formulation, we can view the smooth pasting conditions as reflecting the interests of option holders to maximize their profit. It is a crucial point to note that the delta condition for the American put
	$$
	\fr{\pr v_\text{a}^{\text{put}}}{\pr x}(S^*(t),t) = -1
	$$
is not a by-product of $v_\text{a}^{\text{put}}(S^*(t),t) = K - S^*(t)$. The smooth pasting conditions together are imposed on an American option to ensure the absence of arbitrage opportunities~\cite{Chiarella2014}. Although the delta condition is seldom used in deriving the pricing formulae for American options, it is a necessity when solving the above option pricing PDE numerically (e.g., using the method of lines)~\cite{Chiarella2010}. The value of the asset will dictate what choice the holders should make due to the additional unknown $S^*(t)$ as seen above in the problem formulation. For an American put, the interval $0 \leq x < S^*(t)$ is known as the \emph{exercise region} as it is the most optimal time to exercise the option irrespective of time to expiry since the value of the American put is equal to its payoff. In contrast, $x > S^*(t)$ represents the \emph{continuation region} where the American put is worth more than its payoff and thus is more valuable to continue to hold the option. As we have mentioned in the introduction, the position of $S^*(t)$ (which divides the $x$ domain into the exercise and continuation regions) is unknown \emph{a priori} which adds another layer of difficulty to the option pricing problem.

@@

\section{Useful properties of the CDF of a standard normal variable}
Several properties of the cumulative normal distribution $N$ and its derivative $N'$ will also be required~\cite[pp. 235--239]{Jeff1995}, namely
	\begin{equation}
		\begin{split}
		N(x) = \fr{1}{\sqrt{2\pi}}\int_{-\infty}^x e^{-y^2/2} & \, \d y, \quad %= \fr{1}{2} + \fr{1}{2}\text{erf}\left(\fr{x}{\sqrt{2}}\right) \\
		N(-x) = 1 - N(x), \quad
		N'(x) = \fr{1}{\sqrt{2\pi}}e^{-x^2/2} \label{eqn:Nprime}, \\
		&N(\infty) = 1, \quad N(-\infty) = 0.
		\end{split}
	\end{equation}
We also require the bivariate (standard) normal CDF~\cite{Genz2004}
	\begin{equation}
		\label{eqn:N2}
		N_2(x,y;\rho) = \fr{1}{2\pi\sqrt{1-\rho^2}}\int_{-\infty}^x\int_{-\infty}^y e^{-(u^2-2\rho uv + v^2)/(2(1-\rho^2))} \, \d v \, \d u,
	\end{equation}
where $\rho \in (-1,1)$ . It is not difficult to show that	
	\begin{equation}
		\label{eqn:Nspecial}
		\begin{split}
		&N_2(x,\infty;\rho) = N(x), \quad N_2(\infty,y;\rho) = N(y),\\
		&N_2(x,-\infty;\rho) = N_2(-\infty,y;\rho) = 0, \\
		&N_2(-\infty,\infty;\rho) = N_2(\infty,-\infty;\rho) = 0, \quad N_2(\infty,\infty;\rho) = 1.
		\end{split}
	\end{equation}
\section{Lemmas and corollaries we will need}
The following lemmas and corollaries will also be of great use throughout this thesis:
\subsection{General lemmas}
	\begin{lemma}
		\label{lem:2}
	For $a > 0$ and $b \in \mathbb{R}$, we have
	\begin{equation*}
		\M^{-1}\left\{ e^{-b\xi/a}e^{\xi^2/(2a^2)} \right\} = aN'(a\log x + b).
	\end{equation*}
	\end{lemma}
\begin{proof}
	See Appendix A.1.
\end{proof}
	\begin{lemma}
		\label{lem:1}
		For $a_1, \, a_2 > 0$ and $b_1, \, b_2 \in \mathbb{R}$, we have
			\begin{align*}
				&\int_0^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right).
			\end{align*}
	\end{lemma}
	\begin{proof}
		See Appendix A.2.
	\end{proof}
	\begin{lemma}
		\label{lem:2b}
		For $a_1, \, a_2 > 0$, $b_1, \, b_2 \in \mathbb{R}$, and $c > 0$, it follows that
		\begin{align*}
			&\int_c^\infty \fr{1}{z}N'(a_1\log z + b_1)N'\left(a_2\log\left( 1/z \right) + b_2 \right) \, \d z =  \fr{1}{\sqrt{a_1^2 + a_2^2}}N'\left( \fr{a_1b_2 + a_2b_1}{\sqrt{a_1^2+a_2^2}} \right)N(d),
		\end{align*}
		where
		$$
			d = \sqrt{a_1^2+a_2^2}\left( \log(1/c) + \fr{b_2}{a_2} - \fr{a_1\gamma}{a_1^2+a_2^2} \right), \quad
			\gamma = \fr{a_1b_2}{a_2} + b_1.
		$$
	\end{lemma}
	\begin{proof}
		See Appendix A.3.
	\end{proof}

@@

			e^{\int_{t_1}^{t_2} r(\tau) \, \d\tau}\int_{a_1}^{b_1} \fr{1}{y} \K\left( \fr{x}{y}, t_1, t_2 \right) \, \d y \enskip = N\left( z_2\left( \fr{x}{a_1},t_1,t_2 \right) \right) - N\left( z_2\left( \fr{x}{b_1},t_1,t_2 \right) \right),

@@

			& \qquad  N_2\left( z_2\left( \fr{x}{b_1}, t_1, t_2 \right), z_2\left( \fr{x}{b_2}, t_1, t_3 \right); \rho  \right) + N_2\left( z_2\left( \fr{x}{a_1}, t_1, t_2 \right), z_2\left( \fr{x}{a_2}, t_1, t_3 \right); \rho  \right), \\

@@

where we define $\K_d$ to be the discretised Black-Scholes kernel given by

@@

The expression~\eqref{eqn:Kd} will be very valuable in pricing compound options where the underlying asset pays a single dividend yield.

### 2017-11-09 UOW_thesis_template_v2-0/thesis_template/chapters/jumpImpVol.tex
:art: Adding corrections from Matt Davison

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} are in terms of the strike price $K$. Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x',t; x)$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.

>>>>

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} are with respect to the strike price $K$. Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x',t; x)$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.
